Measuring causal influence with\\ back-to-back regression

### 2019-05-23 paper/synthetic.tex

The data generating process for each experiment constructs $n$ training examples according to the model $Y = \sigma((\text{snr} \cdot XE + N)F)$.
%
Here, 
%\begin{itemize}
%    \item $F \in \mathbb{R}^{d_x \times d_y}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
%    \item $X \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_X)$,
%    \item $N \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_N)$,
%    \item $E \in \mathbb{R}^{d_x \times d_x}$ is a binary diagonal matrix containing $n_c$ ones,
%    \item $\Sigma_X = AA^\top$, where $A \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
%    \item $\Sigma_N = BB^\top$, where $B \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
%\end{itemize}
    $F \in \mathbb{R}^{d_x \times d_y}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
    $X \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_X)$,
    $N \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_N)$,
    $E \in \mathbb{R}^{d_x \times d_x}$ is a binary diagonal matrix containing $n_c$ ones,
    $\Sigma_X = AA^\top$ where $A \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
    $\Sigma_N = BB^\top$ where $B \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
the factor $\text{snr} \in (0, \infty)$, and $\sigma$ is an elementwise function.

To simulate a wide range of experimental conditions, we vary $n \in \{500, 1000, 2000\}$, $d_x, d_y \in \{ 25, 50, 100, 150 \}$, $n_c \in \{ 5, 10 \}$, $\text{snr} \in \{ 0.2, 0.5, 0.75, 1 \}$, and $\sigma \in \{ \text{identity}, \text{sigmoid} \}$.
%
Each condition is simulated under $20$ different random seeds.

@@

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\textwidth]{synthetic.pdf}
    \caption{Results of synthetic experiments. Each dot depicts the average value of a metric for JRR ($x$-axis) against a competitor ($y$-axis) for each experiment configuration, averaged over $20$ random seeds.
    %
    Blue points indicate linear experimental conditions, while orange points indicate nonlinear conditions.}
    \label{table:synthetic}
\end{figure}

>>>>

The data generating process for each experiment constructs $n$ training examples according to the model $Y = (\text{snr} \cdot XE + N)F$.
%
Here, 
%\begin{itemize}
%    \item $F \in \mathbb{R}^{d_x \times d_y}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
%    \item $X \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_X)$,
%    \item $N \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_N)$,
%    \item $E \in \mathbb{R}^{d_x \times d_x}$ is a binary diagonal matrix containing $n_c$ ones,
%    \item $\Sigma_X = AA^\top$, where $A \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
%    \item $\Sigma_N = BB^\top$, where $B \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
%\end{itemize}
    $F \in \mathbb{R}^{d_x \times d_y}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
    $X \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_X)$,
    $N \in \mathbb{R}^{n \times d_x}$ contains rows drawn from $\mathcal{N}(0, \Sigma_N)$,
    $E \in \mathbb{R}^{d_x \times d_x}$ is a binary diagonal matrix containing $n_c$ ones,
    $\Sigma_X = AA^\top$ where $A \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
    $\Sigma_N = BB^\top$ where $B \in \mathbb{R}^{d_x \times d_x}$ contains entries drawn from $\mathcal{N}(0, d_x^{-1})$,
and the factor $\text{snr} \in (0, \infty)$.

To simulate a wide range of experimental conditions, we vary $n \in \{500, 1000, 2000\}$, $d_x, d_y \in \{ 25, 50, 100, 150 \}$, $n_c \in \{ 5, 10 \}$, $\text{snr} \in \{ 0.2, 0.5, 0.75, 1 \}$. 
%
Each condition is simulated under $20$ different random seeds.

@@

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\textwidth]{synthetic.pdf}
    \caption{Results of synthetic experiments. Each dot depicts the average value of a metric for JRR ($x$-axis) against a competitor ($y$-axis) for each experiment configuration, averaged over $20$ random seeds.}
    \label{table:synthetic}
\end{figure}
